\section{Introduction to Mathematical Morphology}
\label{sec:introduction_to_mathematical_morphology}



\setcounter{subsection}{1}
\subsection{Erosion and Dilation}
% question 2 image:
\textbf{Question 1} \textit{Deﬁne erosion and dilatation from an ensemblist point of view and an functional point of view. Give some properties related to these operators.}

In the figure below, the eroded and dilated images can be seen plotted next to the original image for each structuring element with the following shapes in order: rectangle, disk, diamond and line.

\textbf{Question 2} \textit{Operate in a binary image and a greyscale image with the MatLab commands imerode and imdilate. What are the eﬀects on binary and grayscale images? Justify. Try with diﬀerent structuring elements (diﬀerent shapes, diﬀerent sizes).}
% part2_Question2.png


\textbf{Question 3} \textit{Extract internal and external edges of a binary image, and the morphological gradian.}



\textbf{Question 4} \textit{As an exercise, write an algorithm that show, in the map of Europe, the distance of each pixel w.r.t. the sea.}


\textbf{Question 5} \textit{Find an algorithm that detect rectangular objects of ’image2.jpg’.}



\subsection{Morphological Filtering}
\subsubsection{Filters}
\textbf{Question 6} \textit{Deﬁne the two morphological ﬁlters called opening and closing. What are the eﬀects on a binary image sur as ’image1.jpg’ (use the commands imopen and imclose)?}

\subsubsection{Form Detection}
\textbf{Question 7} \textit{The objective being to recognize some forms on images, ﬁnd a simple algorithm to operate form detection}

\textbf{Question 8} \textit{Apply a salt-and-pepper noise: what’s happen with your previous algorithm?}


\subsubsection{Denoising}
\textbf{Question 9} \textit{Use the image Nebuleuse.jpg and apply a salt-and-pepper noise. De-noise the image by ﬁltering.}

\textbf{Question 10} \textit{Apply the same process to the ’Spain Beach’ image to isolate the beach itself.}

\subsubsection{Top-Hat \& Black-Hat Filters}
\textbf{Question 11} \textit{Deﬁne op-hat and black-hat process in a 1D function: what is the associated process?}

\textbf{Question 12} \textit{Deﬁne and operate top-hat and black-hat on a greyscale image. What do you observe?}


\subsection{Morphological Skeletonization \& Segmentation}
\subsubsection{Skeletonization Process}
\textbf{Question 13} \textit{Write and operate a Skeletonization on the diplodocus.}


\textbf{Question 14} \textit{Based on skelittization, ﬁnd an algorithm that operate a segmentation in a binary image. Apply on ’image1.jpg’.}


\subsubsection{Image Segmentation}
\textbf{Question 15} \textit{Find a Skeletonization algorithm and operate on the Blood Cells image.}


